Introduction to Markov state modeling with the PyEMMA software [Article v\versionnumber]

### 2018-11-28 manuscript/manuscript.tex
updating template [ci skip]

\title{Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PUBLICATION INFORMATION
%%% Fill out these parameters when available
%%% These are used when the "pubversion" option is invoked
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pubDOI{10.XXXX/YYYYYYY}
\pubvolume{<volume>}
\pubyear{<year>}
\articlenum{<number>}
\datereceived{July, 27, 2018}
\dateaccepted{Month, Day, Year}

@@

For a more detailed description of author contributions, see the GitHub issue tracking and changelog at \githubrepository{}.

@@

For a more detailed description of contributions from the community and others, see the GitHub issue tracking and changelog at \githubrepository{}.

>>>>

\title{Introduction to Markov state modeling with the PyEMMA software [Article v\versionnumber]}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PUBLICATION INFORMATION
%%% Fill out these parameters when available
%%% These are used when the "pubversion" option is invoked
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pubDOI{10.XXXX/YYYYYYY}
\pubvolume{<volume>}
\pubyear{<year>}
\articlenum{<number>}
\datereceived{Day Month Year}
\dateaccepted{Day Month Year}

@@

For a more detailed description of author contributions,
see the GitHub issue tracking and changelog at \githubrepository.

@@

For a more detailed description of contributions from the community and others,
see the GitHub issue tracking and changelog at \githubrepository.
